Tracing the Stellar Halos of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam

### 2017-06-07 draft/paper1_v11.tex
Alexie's comment: Uncertainties on SMF

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_mass_smf}
      \caption{
          \textbf{Left:} Impact of using \mtot{} on the galaxy stellar mass function. 
          Dashed lines correspond to the SMF computed using \mcmodel{} whereas solid 
          lines correspond to the SMF computed using \mtot{}. 
          Here we separate our HSC sample into  centrals in halos more massive than \logmh{}$\sim14.2$ (red lines) and centrals in 
          halos with \logmh{}$<14.0$ (black lines).
          The impact on the SMF can exceed 0.2 dex for massive central galaxies in 
          very massive halos.
          \textbf{Right}: The stellar mass volume density distributions of massive 
          HSC galaxies, using both \mtot{} (black solid line) and \mmax{} (black dotted 
          line).  The grey  shaded region shows the resampling error on the HSC SMF. We  compaer our results with previous studies: (a): SDSS galaxies at $z{\sim} 0.1$ from \citet{Bernardi2017} with \mstar{} values based on photometry from 2-D \ser{}$+$Exponential model fitting 
          (purple); 
          (b): SDSS galaxies at $z{\sim} 0.1$ from \citet{Moustakas13} based on 
          improved SDSS \texttt{cModel} photometry (blue); 
          (c): \texttt{S82-MGC} galaxies at $0.15 < z< 0.43$ from 
          \citet{Leauthaud2016} based on PSF-matched SDSS-UKIDSS photometry (green).
          Please see text for more details of the comparison.
          }
      \label{fig:smf}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    In this work, we do not attempt to detailed comparison between different SMFs
    \citep[e.g.,][]{Bernardi2013, Bernardi2017} \footnote{To do that, one needs to 
    separate the differences in the measurements of luminosity and \m2l{}, and 
    take the uncertainties of \mstar{} measurements into account}.
    Instead, we primarily aim to visualize the importance of \mstar{} measurements 
    to the SMF at the high-mass end.
    Despite the differences in these SMF, we can see that the ones using 
    \texttt{cModel} or small aperture photometry can not appropriately account for 
    the high-mass end due to the missing light in the outskirt. 
    The $z{\sim}0.1$ GAMA SMF based on single-\ser{} model from \citet{Kelvin2012} 
    appears to have the same issue (\citealt{Wright2017}), although the \ser{} model
    also can overestimate the luminosity at high-mass end\footnote{Due to 
    overestimated \ser{} index and/or effective radius.}.

>>>>

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_mass_smf}
      \caption{
          \textbf{Left:} Impact of using \mtot{} on the galaxy stellar mass function. 
          Dashed lines correspond to the SMF computed using \mcmodel{} whereas solid 
          lines correspond to the SMF computed using \mtot{}. 
          Here we separate our HSC sample into  centrals in halos more massive than
          \logmh{}$\sim14.2$ (red lines) and centrals in halos with \logmh{}$<14.0$ 
          (black lines).
          The impact on the SMF can exceed 0.2 dex for massive central galaxies in 
          very massive halos.
          \textbf{Right}: The stellar mass volume density distributions of massive 
          HSC galaxies, using both \mtot{} (black solid line) and \mmax{} (black dotted 
          line).  
          The grey shaded region shows the resampling error on the HSC SMF plus a 20\%
          uncertainties to account for other issues in our sample. 
          We compare our results with previous studies: 
          (a): SDSS galaxies at $z{\sim} 0.1$ from \citet{Bernardi2017} with \mstar{} 
          values based on photometry from 2-D \ser{}$+$Exponential model fitting 
          (purple); 
          (b): SDSS galaxies at $z{\sim} 0.1$ from \citet{Moustakas13} based on 
          improved SDSS \texttt{cModel} photometry (blue); 
          (c): \texttt{S82-MGC} galaxies at $0.15 < z< 0.43$ from 
          \citet{Leauthaud2016} based on PSF-matched SDSS-UKIDSS photometry (green).
          Please see text for more details of the comparison.
          }
      \label{fig:smf}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    In this work, we do not attempt to detailed comparison between different SMFs
    \citep[e.g.,][]{Bernardi2013, Bernardi2017} \footnote{To do that, one needs to 
    separate the differences in the measurements of luminosity and \m2l{}, and 
    take the uncertainties of \mstar{} measurements into account}.
    Instead, we primarily aim to visualize the importance of \mstar{} measurements 
    to the SMF at the high-mass end.
    We do not include satellite galaxy in our sample (could affect ${\sim}10$\% of 
    galaxies at this very high-mass end) and can not extract 1-D \mden{} profile 
    for a small fraction of galaxies due to severe contamination of nearby object. 
    Therefore, we should expect at least ${\sim}20$\% uncertainties in the current 
    volume density distributions (shown as the shaded region on Fig \ref{fig:smf}).
    Despite the differences in these SMF, we can see that the ones using 
    \texttt{cModel} or small aperture photometry can not appropriately account for 
    the high-mass end due to the missing light in the outskirt. 
    The $z{\sim}0.1$ GAMA SMF based on single-\ser{} model from \citet{Kelvin2012} 
    appears to have the same issue (\citealt{Wright2017}), although the \ser{} model
    also can overestimate the luminosity at high-mass end\footnote{Due to 
    overestimated \ser{} index and/or effective radius.}.
